Agreement Attraction in Turkish

### 2020-09-01 ongoing_draft/ongoing_paper.Rmd
Another merge with PLs version.

---
title             : "Agreement Attraction in Turkish"
shorttitle        : "Agreement Attraction in Turkish"
author: 
  - name          : "Utku Türk"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "utku.turk@boun.edu.tr"
affiliation:
  - id            : "1"
    institution   : "Boğaziçi University University, Istanbul, Turkey"
authornote: |
  authornote
abstract: |
  We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["new-references.bib","r-references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
numbersections    : yes
geometry          : left=25mm, right=25mm, top=25mm, bottom=25mm
#fontsize          : 10pt
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "doc"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
        in_header: paper_draft_preamble.tex
editor_options: 
  chunk_output_type: console
keep_tex: FALSE
keep_md: FALSE
---

@@

library(car, warn.conflicts = FALE)
library(MASS)
library(brms)
library(xtable)
library(ggpubr)

>>>>

---
title             : "Agreement Attraction in Turkish"
shorttitle        : "Agreement Attraction in Turkish"
author: 
  - name          : "Utku Türk"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "utku.turk@boun.edu.tr"
affiliation:
  - id            : "1"
    institution   : "Boğaziçi University University, Istanbul, Turkey"
authornote: |
  authornote
abstract: |
  We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["new-references.bib","r-references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
numbersections    : yes
geometry          : left=25mm, right=25mm, top=25mm, bottom=25mm
#fontsize          : 10pt
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "doc"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
        in_header: paper_draft_preamble.tex
editor_options: 
  chunk_output_type: console
keep_tex: TRUE
keep_md: TRUE
---

@@

library(car, warn.conflicts = FALSE)
library(MASS)
library(brms)
library(xtable)
library(ggpubr)
